\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-05 paper/paper.tex
added template table for results, fixed month of reference
algorithms added for Huub, started on checking grammar

@@

%------------------------------------------------
\section{Algorithms}
\label{algs}
%% TODO %%
% Describe algorithms, show concise calculations of time complexity
%%

%------------------------------------------------
\section{Results}
\label{results}
%% TODO %%
% Give and describe results
%%

@@

\begin{appendices}
\label{appendices}
\end{appendices}
%----------------------------------------------------------------------------------------

>>>>

% Additional column type
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

@@

%------------------------------------------------
\section{Algorithms}
\label{algs}
%% TODO %%
% Describe algorithms, show concise calculations of time complexity
%%
For the paper, two different color refinement methods were implemented. The basic one gives all vertices in a graph with the same color but differently colored neighborhoods a separate color. This is done iteratively until the graph is stably colored. A coloring $\alpha$ of $G$ is stable if for all $u, v \in V(G)$ it holds that: if $\alpha(u) = \alpha(v)$, then $u$ and $v$ have identically colored neighborhoods. The problem with this method is that all vertices are checked each iteration. With fast color refinement the colors that lead to refinements are tracked. These colors are maintained in a queue. If a color class is being refined, the class is split into two different classes, with one class keeping the old color. The algorithm terminates with a stable color if no color class needs refinement in other words the queue is empty. The initial coloring is done in a separate algorithm before the color refinement algorithms take place and is therefore the same for both the fast and basic implementation.
Computing time of our algorithms are increasing by iterations over the vertices in a graph. To calculate the time complexity of the algorithms, the number of and the places of the iterations over the vertices are analyzed. In the basic implementation are several places where iterations over vertices take place. The code contains one main loop that takes worst case N iterations. So the time complexity so far is $O(\boldsymbol{N})$ In this main loop an iteration takes place over all the vertices in the graph. Time complexity is $O(N \cdot \boldsymbol{N})$ now. Each vertex is checked if it needs an update. If so, a new color dictionary is made and a new loop over the dictionary takes place. The time complexity is $O(N \cdot N \cdot \boldsymbol{N})$ for making the dictionary and gets $O((N \cdot N)(N+\boldsymbol{N}))$ for iterating over the dictionary. For each item in the dictionary is checked if the configuration already is assigned a new color. If the the configuration is not know yet, a new color is assigned. In worst case this new color operation costs again N. The time complexity is $O((N \cdot N)(N+N+\boldsymbol{N}))$ so far.
After the first loop over the vertices in the main loop, again the algorithm iterates over all the vertices to color all the vertices correctly in the main dictionary. The time complexity worst case at the end is $O((N \cdot (N+\boldsymbol{N})(N+N+N)) = O(N^3)$

%------------------------------------------------
\section{Results}
\label{results}
%% TODO %%
% Give and describe results
%%
% Table for results can be found at appendices

@@

\begin{appendices}
\label{app}

%------------------------------------------------
\section{Tables} %Change section name
\label{app:tab}
%% TODO %%
% Fill table with actual values
%%
%% NOTE %%
% All current values are fictional values for testing purposes only
%%
\begin{table}[h]\centering
\label{app:tab:0}
\begin{tabular}{|l|r@{.}l|r@{.}l|}
\hline
Graph	
	& \multicolumn{2}{l|}{Algorithm A \emph{(s)}}
	& \multicolumn{2}{l|}{Algorithm B \emph{(s)}} \\
\hline
graph\_{}type1\_{}16
	& 0	& 001
	& 0	& 005 \\
graph\_{}type1\_{}64
	& 0	& 1	
	& 0	& 1 \\
graph\_{}type1\_{}256
	& 10	& 0	
	& 2		& 0\\
graph\_{}type1\_{}1024
	& 1000	& 0 
	& 40	& 0 \\
graph\_{}type1\_{}4096
	& 100000	& 0
	& 800		& 0 \\
\hline
\end{tabular}
\caption{This is a table}
\end{table}
%------------------------------------------------

\end{appendices}
%----------------------------------------------------------------------------------------
